Inattentive responding can induce spurious associations between task behavior and symptom measures

### 2023-01-17 manuscripts/letter.tex
ready for resubmission (probably)

In addition, if these results are not yet sufficient to ease your mind regarding psychiatric overcontrol, in another new study that we detail on in response to your critique 3 below, we tested a new sample for correlations between self report of non-symptom measures (greed avoidance and artistic interests), and also found these measures to have spurious correlations with task performance when no C/IE screening was applied. Since there is no reason to expect that the correlation is specifically driven by psychopathology, an overcontrol of those suffering from psychiatric conditions should not have affected these correlations in the way it did. See more details below, and in Appendix B of the paper.

@@

We respectfully disagree with the reviewer's view that the results here lack novelty (see also response to Reviewer 1, point \#2). Though the perils of C/IE responding for individual-differences questionnaire research has been documented before \cite{chandler2020participant, arias2020little}, we are unaware of any manuscript prior to ours addressing the risk of spurious correlations from C/IE responding for individual-differences cognitive science research (including computational psychiatry). To this point, our literature review revealed that, whereas the majority of behavioral researchers were applying quality controls to their behavioral data, only the minority of researchers were doing the same for their self-report data (and fewer still were following best practices). This suggests that, although behavioral researchers were aware of the need for data quality assurance protocols in general, few in this growing and impactful field were aware of the need for rigorous screening of their self-report data. Importantly, this may have already led to spurious results in the field. If it were commonly accepted that correlations between unusually high symptom levels on psychiatric measures and performance on behavioral measures are not meaningful, this would have been a cornerstone in the field of computational psychiatry, as this field is predominantly interested in such correlations. Nevertheless, we had not heard of this idea prior to doing our own research on the matter.

@@

If by ``MTurk/Prolific scores'' the reviewer is referring to platform-specific metrics like HIT Approval Rate, we did not use these as inclusion criteria because previous research has found they are not discriminating between low- and high-quality participants \cite{robinson2019tapped}. This is noted in the methods under the ``Sample'' section:

>>>>

@@

We respectfully disagree with the reviewer's view that the results here lack novelty (see also response to Reviewer 1, point \#2). Though the perils of C/IE responding for individual-differences questionnaire research has been documented before \cite{chandler2020participant, arias2020little}, we are unaware of any manuscript prior to ours addressing the risk of spurious correlations from C/IE responding for individual-differences cognitive science research (including computational psychiatry). To this point, our literature review revealed that, whereas the majority of behavioral researchers were applying quality controls to their behavioral data, only the minority of researchers were doing the same for their self-report data (and fewer still were following best practices). This suggests that, although behavioral researchers were aware of the need for data quality assurance protocols in general, few in this growing and impactful field were aware of the need for rigorous screening of their self-report data.

@@

If by ``MTurk/Prolific scores'' the reviewer is referring to platform-specific metrics like HIT Approval Rate, we did not use these as inclusion criteria because previous research has found they are not discriminating between low- and high-quality participants \cite{robinson2019tapped}. This is already noted in the methods under the ``Sample'' section:

### 2023-01-17 manuscripts/main.tex
ready for resubmission (probably)

@@

% make abstract
\abstract{
A common research design in the field of computational psychiatry involves leveraging the power of online participant recruitment to assess correlations between behavior in cognitive tasks and the self-reported severity of psychiatric symptoms in large, diverse samples. Although large online samples have many advantages for psychiatric research, some potential pitfalls of this research design are not widely understood. Here we detail circumstances in which entirely spurious correlations may arise between task behavior and symptom severity as a result of inadequate screening of careless or low-effort responding on psychiatric symptom surveys. Specifically, since many psychiatric symptom surveys have asymmetric ground-truth score distributions in the general population, participants who respond carelessly on these surveys will show apparently elevated symptom levels. If these participants are similarly careless in their task performance, and are not excluded from analysis, this may result in a spurious association between greater symptom scores and worse behavioral task performance. Here, we demonstrate exactly this pattern of results in $N = 386$ participants recruited online to complete a self-report symptom battery and a short reversal-learning choice task. We show that many behavior-symptom correlations are entirely abolished when participants flagged for careless responding on surveys are excluded from analysis. We also show that exclusion based on task performance alone is not sufficient to prevent these spurious correlations. Of note, we demonstrate that false-positive rates for these spurious correlations \emph{increase} with sample size, contrary to common assumptions. We offer guidance on how researchers using this general experimental design can guard against this issue in future research; in particular, we recommend the adoption of screening methods for self-report measures that are currently uncommon in this field.
}

@@

To measure the correspondence of screening measures estimated from task and self-report behavior, we conducted an online behavioral experiment involving a simple decision-making task and a battery of commonly used self-report psychiatric symptom measures (see Methods). A final sample of 386 participants from the Amazon Mechanical Turk (N=186) and Prolific (N=200) online labour markets completed a probabilistic reversal-learning task and 5 self-report symptom measures. The reversal-learning task required participants to learn through trial-and-error which of three options yielded reward most often, and was modeled after similar tasks used to probe reinforcement-learning deficits in psychiatric disorders \cite{waltz2007probabilistic, mukherjee_reward_2020}. The five self-report symptom measures were the 7-up (which measures symptoms of hypomania), the 7-down (which measures symptoms of depression), the GAD-7, (which measures generalized anxiety symptoms), the BIS/BAS (which measures reward and punishment motivations), the SHAPS (which measures anhedonia symptoms), and the PSWQ (which measures worry symptoms), and were chosen based on previous literature to have a variety of expected response distributions (symmetric and asymmetric). In line with current best-practice recommendations in personality psychology \cite{huang2015detecting}, each self-report instrument included one `infrequency' item that could be used to identify C/IE responses in survey data (see Methods for a list of infrequency items). The entire experiment (surveys and task) was designed to require 10 minutes on average to complete (observed mean = 10.28 minutes). To minimize any influence of fatigue on survey responding, participants completed the surveys prior to beginning the task.

@@

Second, we used the Dice similarity coefficient to quantify agreement between different screening methods in the set of participants flagged for exclusion (Figure \ref{fig:correspondence}, right panel). This approach quantifies the degree of overlap between the set of would-be excluded participants based on different screening measures under a common exclusion rate. Though some measures have relatively clear threshold cutoffs (e.g., chance level performance for task accuracy), the majority of the measures evaluated here do not. As such, we evaluated the measures with respect to the top 10\% of ``suspect" participants flagged by each measure, corresponding roughly to the fraction of participants having performed at chance levels on the reversal-learning task \footnote{Results of the same analysis repeated for the top 25\% of ``suspicious" participants (corresponding roughly to the fraction of participants flagged by the infrequency-item measure) produced similar results, and are included in the supplement.}. Results were largely consistent with the correlation analysis: few pairs of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance. The only significant cross-modality pair identified --- between the infrequency item and choice accuracy measures --- has a similarly coefficient less than 0.4. In other words, when these two measures are used to identify the top 10\% of participants most strongly suspected of C/IE responding, they agree on only two out of every five participants. Screening on choice accuracy alone (the most common method identified in our literature review) would fail to identify the majority of participants most likely engaging in C/IE responding as determined by the infrequency items.

@@

\begin{figure}[!t]
\includegraphics[width=17cm]{../figures/main_03a.png}
\centering
\captionsetup{width=0.88\textwidth}
\caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions. Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; \hl{all signed correlations are shown in the Supplementary Figure} \ref{fig:correlations_s1}). Black Xs indicate significant correlations ablated under screening. No Screening = no exclusions; Accuracy Only = exclusions based on chance-level performance in the reversal-learning task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures. Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
\label{fig:correlations}
\end{figure}

@@

In the self-report symptom measures, we replicated the finding that total scores were noticeably exaggerated in participants suspected of C/IE responding, but only for symptom measures where overall rates of symptom endorsement were the lowest (i.e., measures that have normative endorsements skewed towards 0). Similarly, we again found that task-based screening and self-report screening measures showed low correspondence; that is, excluding participants on the basis of poor behavioral performance would not have identified and removed participants who engaged in C/IE responding on self-report surveys.

@@

To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder (see Appendix C for details). Specifically, N=45 psychiatric patients (confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview) and N=20 healthy controls, all recruited through the Rutgers-Princeton Center for Computational Cognitive NeuroPsychiatry (i.e., personal recruitment, not on online platforms), completed a series of self-report symptom measures, online, on their computers from the comfort of their homes. In total, 16 of 65 (24.6\%) participants failed one or more attention checks. Subdivided by group, 6 of 20 (30\%) healthy participants and 10 of 45 (22\%) psychiatric participants were flagged for C/IE responding.

@@

One way of conceptualizing our results is through the lens of rational allocation of mental effort \cite{kool2018mental}. In any experiment, attentive responding is more effortful than careless responding. As such, participants completing an online task must perform a cost-benefit analysis---implicitly or otherwise---to decide how much effort to exert in responding. The variables that factor into such calculations are presumably manifold and likely include features of the experiment (e.g., task difficulty, monetary incentives), facets of the participant (e.g., subjective effort costs, intrinsic motivation, conscientiousness), and features of the online labor market itself (e.g., opportunity costs, repercussions for careless responding).

Viewed from the perspective of effort expenditure, our results suggest that participants appraised the cost/benefit trade-off differently for behavioral tasks and self-report surveys. Specifically, we found that only 7\% of participants were at chance-level performance in our task, compared to more than 22\% of participants who failed one or more attention-check items in the self-report surveys \hl{(a finding that replicated in a second study involving a different task)}. Moreover, different measures of C/IE responding were weakly or not at all correlated between task behavior and self-report responses. This suggests the motivation for effortful responding was greater in the behavioral task, though precisely why is unclear. One possibility is that we gave participants a monetary incentive for attentive responding only during the task (a common practice, according to our literature review). A second possibility is that participants expected fewer consequences for C/IE responding during the self-report surveys, a reasonable assumption in light of how infrequently previous experiments have screened self-report data. Alternatively, participants may have found the gamified behavioral task more engaging or the self-report inventory more tedious. Regardless of the reason, this discrepancy reinforces our observations concerning the inadequacy of behavioral-task screening as a stand-alone method for identifying C/IE responding. Since, in general, participants may appraise costs and benefits of effortful responding differently for behavioral tasks and self-report surveys, screening for C/IE responding on one data modality may in general be unsuitable for identifying it in the other. We therefore recommend screening on each component of an experiment.

@@

There are several notable limitations to this proof-of-concept study. We used a small set of screening measures, and did not employ other recommended procedures (e.g. logging each key/mouse interaction during survey administration to detect form-filling software or other forms of speeded responding \cite{buchanan2018methods}). Thus, we cannot be confident that all of the flagged participants were indeed engaging in C/IE responding; similarly, we cannot be certain that we correctly excluded all participants engaged in C/IE responding. We studied behavior-symptom correlations for only two tasks and a small self-report symptom batteries. It remains to be seen how generalizable our findings are, although our study design was inspired by experiments prevalent in the online computational psychiatry literature. As suggested above, future studies may find greater correspondence between task and self-report screening measures for more difficult behavioral experiments. Finally, we should note that, unlike previous studies in which some participants were explicitly instructed to respond carelessly \cite{buchanan2018methods}, we do not have access to ``ground truth'' regarding which participants were engaging in C/IE responding. Future work testing the efficacy of different screening metrics for identifying instructed C/IE responding may help to identify some of the issues that we have identified here.

@@

To characterize common data screening practices in online computational psychiatry studies, we performed a narrative literature review \cite{grant2009typology}. We identified studies for inclusion through searches on Google Scholar using permutations of query terms related to online labour platforms (e.g. ``mechanical turk", ``prolific", ``online"), experimental paradigms (e.g. ``experiment", ``cognitive control", ``reinforcement learning"), and symptom measures (e.g. ``psychiatry", ``mental illness", ``depression"). \hl{We note that it was not feasible to conduct a systematic review, which requires the use of a publication database with reproducible search, because we required Google Scholar's full-text search in order to identify papers by recruitment method (e.g., Mechanical Turk).} We included in the review studies that (a) recruited participants online through a labour platform, (b) measured behavior on at least one experimental task, and (c) measured responses on at least one self-report symptom measure. Through this approach, we identified for inclusion 49 studies spanning 2015 through 2020. The complete list of studies, and search terms used to find them, are included in the Github repository for this study.

@@

Here we report a conceptual replication of our original study. The motivations for conducting a replication study were threefold. First, we wanted to examine the generalizability of our findings under new labor-platform conditions. Since summer 2020, when the original data were collected, online labor markets like Mechanical Turk/CloudResearch and Prolific Academic have undergone important changes. To address rampant data quality issues on Mechanical Turk, CloudResearch introduced their ``Approved Participants'' filter. When selected, only Mechanical Turk participants with a prior history of attentive and careful work are invited to participate in experiments \cite{cloudresearch_2020-2, hauser2021evaluating}. Similarly, a deluge of new, lower-quality users signed up to participate in studies on Prolific in summer, 2021 \cite{Letzter2021-bw}. In response, Prolific introduced new controls and filters to improve data quality on the platform \cite{prolific_2021}. In the wake of these changes, we wanted to explore the relevance of our original findings. Specifically, with these new safeguards, we wanted to examine whether the chance of spurious correlations has been considerably reduced.

@@

Here we reported findings from a replication study whose purpose was to examine the generalizability of our original findings under new labor market conditions, different behavioral measures, and different self-report measures. To this end, we recruited an independent sample of almost 400 participants, using CloudResearch's and Prolific's latest data-quality filters, to complete the two-step task and a novel set of self-report measures. As evidence of the efficacy of the new data-quality filters, the proportion of participants flagged for C/IE responding in the self-report measures was noticeably smaller in the replication sample (14\%) compared to original sample (22\%). This decrease in the number of participants suspected of C/IE responding was observed for both MTurk and Prolific (though, as in the original study, the proportion of low-quality participants was significantly, albeit marginally, smaller for Prolific than MTurk). Regardless, although the new online labor platform quality-control measures seem to be effective, they did not completely solve the problem; indeed, the proportion of participants engaging in C/IE responding was reduced only by one-third.

@@

In summary, we conclude that the results of the original study are not limited to the task and self-report measures used in that study, or to online platforms at a particular point in time. Despite legitimate advances in data quality controls, online labor platforms still suffer from participants engaging in C/IE responding. Given \textit{a priori} uncertainty regarding the ability of task measures alone to screen such participants, we recommend also using infrequency items to detect inattentive responding on self-report measures. Finally, and most importantly, this second study strengthened the finding that C/IE responding is likely to result in mean-shifts in scores for symptom scales with overall low rates of endorsement, which are in turn capable of yielding spurious correlations between self-report and behavioral measures. The best safeguard against such spurious correlations continues to be screening in both domains.

@@

In both studies, participants volunteered for a 3-session study conducted online via video conferencing. Specifically, participants completed each session from their homes while on Zoom with a study coordinator. During each session, while participants were completing self-report questionnaires or behavioral tasks, the study coordinator turned off their camera and microphone, but was available if the participant had any questions.

Participants were recruited through clinician referral and Google ads targeting individuals with a history of depression, anhedonia, apathy, and/or (hypo)mania symptoms. Participants were eligible for participation if they (1) had no history of head injury resulting in loss of consciousness for more than 20 minutes; (2) had not been diagnosed with intellectual disability; (3) had not been diagnosed with any neurological condition; (4) did not meet criteria for substance dependence (excluding nicotine) in the past 6 months; (5) had not received electroconvulsive therapy in the past 8 weeks; and (6) were aged between 18-65. For one of the two studies, participants were also required to score 6 or higher on the Wechsler Test of Adult Reading to be included in the study. Furthermore, clinical participants were eligible if they met criteria for a diagnosis of major depressive disorder and, if they were on medication, they had been on on stable treatment with this medication for at least the past 4 weeks. Non-clinical (control group) participants were eligible if they did not meet criteria for any psychiatric diagnosis and were not currently taking any medication used to treat psychiatric disorders.

@@

\begin{enumerate}
    \item Worrying too much about the 1977 Olympics.
    \item I have never used a computer.
    \item I would be able to lift a small (1 lb) weight.
    \item Have there been times of a couple days or more when you were able to stop breathing entirely (without the aid of medical equipment)?
    \item Over the past year, how often did you have days where you were able to blink your eyes without difficulty?
    \item I am generally able to remember my own name.
\end{enumerate}

>>>>

% define highlight style
\colorlet{usercolorname}{yellow!00}    % use for public version
% \colorlet{usercolorname}{yellow!30}    % use for reviewer version
\sethlcolor{usercolorname}

@@

% make abstract
\abstract{
A common research design in the field of computational psychiatry involves leveraging the power of online participant recruitment to assess correlations between behavior in cognitive tasks and the self-reported severity of psychiatric symptoms in large, diverse samples. Although large online samples have many advantages for psychiatric research, some potential pitfalls of this research design are not widely understood. Here we detail circumstances in which entirely spurious correlations may arise between task behavior and symptom severity as a result of inadequate screening of careless or low-effort responding on psychiatric symptom surveys. Specifically, since many psychiatric symptom surveys have asymmetric ground-truth score distributions in the general population, participants who respond carelessly on these surveys will show apparently elevated symptom levels. If these participants are similarly careless in their task performance, and are not excluded from analysis, this may result in a spurious association between greater symptom scores and worse behavioral task performance. Here, we demonstrate exactly this pattern of results in \hl{two independent samples of participants (total $N = 779$)} recruited online to complete a self-report symptom battery and \hl{one of two common cognitive tasks}. We show that many behavior-symptom correlations are entirely abolished when participants flagged for careless responding on surveys are excluded from analysis. We also show that exclusion based on task performance alone is \hl{often insufficient} to prevent these spurious correlations. Of note, we demonstrate that false-positive rates for these spurious correlations \emph{increase} with sample size, contrary to common assumptions. We offer guidance on how researchers using this general experimental design can guard against this issue in future research; in particular, we recommend the adoption of screening methods for self-report measures that are currently uncommon in this field.
}

@@

To measure the correspondence of screening measures estimated from task and self-report behavior, we conducted an online behavioral experiment involving a simple decision-making task and a battery of commonly used self-report psychiatric symptom measures (see Methods). A final sample of 386 participants from the Amazon Mechanical Turk (N=186) and Prolific (N=200) online labour markets completed a probabilistic reversal-learning task and 5 self-report symptom measures. The reversal-learning task required participants to learn through trial-and-error which of three options yielded reward most often, and was modeled after similar tasks used to probe reinforcement-learning deficits in psychiatric disorders \cite{waltz2007probabilistic, mukherjee_reward_2020}. The five self-report measures were the 7-up (which measures symptoms of hypomania), the 7-down (which measures symptoms of depression), the GAD-7, (which measures generalized anxiety symptoms), the BIS/BAS (which measures reward and punishment motivations), the SHAPS (which measures anhedonia symptoms), and the PSWQ (which measures worry symptoms), and were chosen based on previous literature to have a variety of expected response distributions (symmetric and asymmetric). In line with current best-practice recommendations in personality psychology \cite{huang2015detecting}, each self-report instrument included one `infrequency' item that could be used to identify C/IE responses in survey data (see Methods for a list of infrequency items). The entire experiment (surveys and task) was designed to require 10 minutes on average to complete (observed mean = 10.28 minutes). To minimize any influence of fatigue on survey responding, participants completed the surveys prior to beginning the task.

@@

Second, we used the Dice similarity coefficient to quantify agreement between different screening methods in the set of participants flagged for exclusion (Figure \ref{fig:correspondence}, right panel). This approach quantifies the degree of overlap between the set of would-be excluded participants based on different screening measures under a common exclusion rate. Though some measures have relatively clear threshold cutoffs (e.g., chance level performance for task accuracy), the majority of the measures evaluated here do not. As such, we evaluated the measures with respect to the top 10\% of ``suspect" participants flagged by each measure, corresponding roughly to the fraction of participants having performed at chance levels on the reversal-learning task.\footnote{Results of the same analysis repeated for the top 25\% of ``suspicious" participants (corresponding roughly to the fraction of participants flagged by the infrequency-item measure) produced similar results, and are included in the supplement.} Results were largely consistent with the correlation analysis: few pairs of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance. The only significant cross-modality pair identified --- between the infrequency item and choice accuracy measures --- has a similarly coefficient less than 0.4. In other words, when these two measures are used to identify the top 10\% of participants most strongly suspected of C/IE responding, they agree on only two out of every five participants. Screening on choice accuracy alone (the most common method identified in our literature review) would fail to identify the majority of participants most likely engaging in C/IE responding as determined by the infrequency items.

@@

\begin{figure}[!t]
\includegraphics[width=17cm]{../figures/main_03a.png}
\centering
\captionsetup{width=0.88\textwidth}
\caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions. Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; \hl{all signed correlations are shown in Supplementary Figure} \ref{fig:correlations_s1}). Black Xs indicate significant correlations ablated under screening. No Screening = no exclusions; Accuracy Only = exclusions based on chance-level performance in the reversal-learning task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures. Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
\label{fig:correlations}
\end{figure}

@@

In the self-report symptom measures, we replicated the finding that total scores were noticeably exaggerated in participants suspected of C/IE responding, but only for symptom measures where overall rates of symptom endorsement were the lowest. Similarly, we again found that task-based screening and self-report screening measures showed low correspondence; that is, excluding participants on the basis of poor behavioral performance would not have identified and removed participants who engaged in C/IE responding on self-report surveys.

@@

To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder (see Appendix C for details). Specifically, N=45 psychiatric patients (confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview) and N=20 healthy controls, all recruited through the Rutgers-Princeton Center for Computational Cognitive Neuropsychiatry (i.e., personal recruitment, not on online labour platforms), completed a series of self-report symptom measures, online, on their computers from the comfort of their homes. In total, 16 of 65 (24.6\%) participants failed one or more attention checks. Subdivided by group, 6 of 20 (30\%) healthy participants and 10 of 45 (22\%) psychiatric participants were flagged for C/IE responding.

@@

One way of conceptualizing our results is through the lens of rational allocation of mental effort \cite{kool2018mental}. In any experiment, attentive responding is more effortful than careless responding. As such, participants completing an online task must perform a cost-benefit analysis---implicitly or otherwise---to decide how much effort to exert in responding. The variables that factor into such calculations are presumably manifold and likely include features of the experiment (e.g., task difficulty, monetary incentives), facets of the participant (e.g., subjective effort costs, intrinsic motivation, conscientiousness), and features of the online labour market itself (e.g., opportunity costs, repercussions for careless responding).

Viewed from the perspective of effort expenditure, our results suggest that participants appraised the cost/benefit trade-off differently for behavioral tasks and self-report surveys. Specifically, we found that only 7\% of participants were at chance-level performance in our task, compared to more than 22\% of participants who failed one or more attention-check items in the self-report surveys \hl{(a finding that qualitatively replicated in a second study involving a different task)}. Moreover, different measures of C/IE responding were weakly or not at all correlated between task behavior and self-report responses. This suggests the motivation for effortful responding was greater in the behavioral task, though precisely why is unclear. One possibility is that we gave participants a monetary incentive for attentive responding only during the task (a common practice, according to our literature review). A second possibility is that participants expected fewer consequences for C/IE responding during the self-report surveys, a reasonable assumption in light of how infrequently previous experiments have screened self-report data. Alternatively, participants may have found the gamified behavioral task more engaging or the self-report inventory more tedious. Regardless of the reason, this discrepancy reinforces our observations concerning the inadequacy of behavioral-task screening as a stand-alone method for identifying C/IE responding. Since, in general, participants may appraise costs and benefits of effortful responding differently for behavioral tasks and self-report surveys, screening for C/IE responding on one data modality may in general be unsuitable for identifying it in the other. We therefore recommend screening on each component of an experiment.

@@

There are several notable limitations to this proof-of-concept study. We used a small set of screening measures, and did not employ other recommended procedures (e.g. logging each key/mouse interaction during survey administration to detect form-filling software or other forms of speeded responding \cite{buchanan2018methods}). Thus, we cannot be confident that all of the flagged participants were indeed engaging in C/IE responding; similarly, we cannot be certain that we correctly excluded all participants engaged in C/IE responding. We studied behavior-symptom correlations for only two tasks and two short self-report symptom batteries. It remains to be seen how generalizable our findings are, although our study design was inspired by experiments prevalent in the online computational psychiatry literature. As suggested above, future studies may find greater correspondence between task and self-report screening measures for more difficult behavioral experiments. Finally, we should note that, unlike previous studies in which some participants were explicitly instructed to respond carelessly \cite{buchanan2018methods}, we do not have access to ``ground truth'' regarding which participants were engaging in C/IE responding. Future work testing the efficacy of different screening metrics for identifying instructed C/IE responding may help to identify some of the issues that we have identified here.

@@

To characterize common data screening practices in online computational psychiatry studies, we performed a narrative literature review \cite{grant2009typology}. We identified studies for inclusion through searches on Google Scholar using permutations of query terms related to online labour platforms (e.g. ``mechanical turk", ``prolific", ``online"), experimental paradigms (e.g. ``experiment", ``cognitive control", ``reinforcement learning"), and symptom measures (e.g. ``psychiatry", ``mental illness", ``depression"). \hl{We note that it was not feasible to conduct a systematic review, which requires the use of a publication database with reproducible search, because we required Google Scholar's full-text search in order to identify papers by recruitment method (e.g., Mechanical Turk).} We included in the review studies that (a) recruited participants online through a labour platform, (b) measured behavior on at least one experimental task, and (c) measured responses on at least one self-report symptom measure. Through this approach, we identified for inclusion 49 studies spanning 2015 through 2020. \hl{The complete list of studies, and search terms used to find them, are included in the Github repository for this study.}

@@

Here we report a conceptual replication of our original study. The motivations for conducting a replication study were threefold. First, we wanted to examine the generalizability of our findings under new labour-platform conditions. Since summer 2020, when the original data were collected, online labour markets like Mechanical Turk/CloudResearch and Prolific Academic have undergone important changes. To address rampant data quality issues on Mechanical Turk, CloudResearch introduced their ``Approved Participants'' filter. When selected, only Mechanical Turk participants with a prior history of attentive and careful work are invited to participate in experiments \cite{cloudresearch_2020-2, hauser2021evaluating}. Similarly, a deluge of new, lower-quality users signed up to participate in studies on Prolific in summer, 2021 \cite{Letzter2021-bw}. In response, Prolific introduced new controls and filters to improve data quality on the platform \cite{prolific_2021}. In the wake of these changes, we wanted to explore the relevance of our original findings. Specifically, with these new safeguards, we wanted to examine whether the chance of spurious correlations has been considerably reduced.

@@

Here we reported findings from a replication study whose purpose was to examine the generalizability of our original findings under new labour market conditions, different behavioral measures, and different self-report measures. To this end, we recruited an independent sample of almost 400 participants, using CloudResearch's and Prolific's latest data-quality filters, to complete the two-step task and a novel set of self-report measures. As evidence of the efficacy of the new data-quality filters, the proportion of participants flagged for C/IE responding in the self-report measures was noticeably smaller in the replication sample (14\%) compared to original sample (22\%). This decrease in the number of participants suspected of C/IE responding was observed for both MTurk and Prolific (though, as in the original study, the proportion of low-quality participants was significantly, albeit marginally, smaller for Prolific than MTurk). Regardless, although the new online labour platform quality-control measures seem to be effective, they did not completely solve the problem; indeed, the proportion of participants engaging in C/IE responding was reduced only by one-third.

@@

In summary, we conclude that the results of the original study are not limited to the task and self-report measures used in that study, or to online platforms at a particular point in time. Despite legitimate advances in data quality controls, online labour platforms still suffer from participants engaging in C/IE responding. Given \textit{a priori} uncertainty regarding the ability of task measures alone to screen such participants, we recommend also using infrequency items to detect inattentive responding on self-report measures. Finally, and most importantly, this second study strengthened the finding that C/IE responding is likely to result in mean-shifts in scores for symptom scales with overall low rates of endorsement, which are in turn capable of yielding spurious correlations between self-report and behavioral measures. The best safeguard against such spurious correlations continues to be screening in both domains.

@@

In both studies, participants volunteered for a multi-session study conducted online via video conferencing. Specifically, participants completed each session from their homes while on Zoom with a study coordinator. During each session, while participants were completing self-report questionnaires or behavioral tasks, the study coordinator turned off their camera and microphone, but was available if the participant had any questions.

Participants were recruited through clinician referral and online ads (i.e., Google ads, Craigslist) targeting individuals with a history of depression, anhedonia, apathy, and/or (hypo)mania symptoms. Participants were eligible for participation if they (1) had no history of head injury resulting in loss of consciousness for more than 20 minutes; (2) had not been diagnosed with intellectual disability; (3) had not been diagnosed with any neurological condition; (4) did not meet criteria for substance dependence (excluding nicotine) in the past 6 months; (5) had not received electroconvulsive therapy in the past 8 weeks; and (6) were aged between 18-65. For one of the two studies, participants were also required to score 6 or higher on the Wechsler Test of Adult Reading to be included in the study. Furthermore, clinical participants were eligible if they met criteria for a diagnosis of major depressive disorder and, if they were on medication, they had been on on stable treatment with this medication for at least the past 4 weeks. Non-clinical (control group) participants were eligible if they did not meet criteria for any psychiatric diagnosis and were not currently taking any medication used to treat psychiatric disorders.

@@

\begin{enumerate}
    \item Worrying too much about the 1977 Olympics. (Expected response: \textit{Not at all})
    \item I have never used a computer. (Expected response: \textit{Completely untrue} or \textit{Quite untrue})
    \item I would be able to lift a small (1 lb) weight. (Expected response: \textit{Extremely characteristic of me} or \textit{Somewhat characteristic of me})
    \item Have there been times of a couple days or more when you were able to stop breathing entirely (without the aid of medical equipment)? (Expected response: \textit{Never})
    \item Over the past year, how often did you have days where you were able to blink your eyes without difficulty? (Expected response: \textit{Often} or \textit{Very often})
    \item I am generally able to remember my own name. (Expected response: \textit{True})
\end{enumerate}
